---
title: "Homework 1.5"
format: 
  html: 
    self-contained: true
    embed-resources: true
editor: visual
---

::: {.callout-note icon="false"}
#### Task - Load a CSV

1.  Attach the readr package using `library()`.
2.  Load `laryngoscope-clean.csv` from the `data` folder using `read_csv()`. If you get an error, make sure you have quotation marks around the file name, that this homework file is in your session 1 folder, and that `read_csv()` is looking in the `data` folder.
3.  Assign the result to an object called `laryngoscope`.

```{r}
# your code here 
```
:::

::: {.callout-tip collapse="true"}
#### Solution - Load a CSV

```{r}
#| output: false
#| label: answer-load-csv
library(readr)
laryngoscope <- read_csv("data/laryngoscope-clean.csv")
```
:::

::: {.callout-note icon="false"}
#### Task - Get a column's values

The laryngoscope data describe 99 patients who received orotracheal intubation.

1.  Check the data frame's variable names with the `names()` function.
2.  Use the `$` selector to get the `attempt1_time` variable's values in seconds.
3.  Calculate the mean of these values, rounded to two decimal places.

```{r}
# ðŸ¡
# your code here 
```
:::

::: {.callout-tip collapse="true"}
#### Solution - Get a column's values

```{r}
#| output: false
#| label: answer-get-column
# 1
names(laryngoscope)
# 2
laryngoscope$attempt1_time
# 3
round(mean(laryngoscope$attempt1_time), 2)
```

The mean is 33.41 seconds.
:::

::: {.callout-note icon="false"}
#### Task - More arithmetic

\(1\) Consider the heights and weights from a different set of patients below. Let's compare their BMIs to the laryngoscope patients. BMI is given by: $\mathrm{BMI} = \frac{\mathrm{weight}(kg)}{\mathrm{height}(m)^2}$ . Convert `weight_lbs` into kg and assign it to `weight_kg`.

\(2\) Convert and assign `height_in` into `height_m`.

\(3\) Calculate BMI using the metric values, `weight_kg` and `height_m`, using the formula above. Assign to an object named `bmi_2`. ("BMI 1" are the values in `laryngoscope`.)

\(4\) Check the metric BMIs you have calculated, against the formula for BMI with imperial measurements, using `weight_lbs` and `height_in`. $\mathrm{BMI} = 703 \times \frac{\mathrm{weight}(lbs)}{\mathrm{height}(in)^2}$ .

\(5\) Calculate the mean of your BMIs, and compare them to the mean BMI in `laryngoscope`. Does this second group of patients have a higher a lower mean BMI than the laryngoscope patients? (Note: we don't know whether this difference is *significant* or coincidental without further work!)

```{r}
weight_lbs <- c(127.0, 147.7, 262.2, 248.9, 152.0, 217.7)
height_in <- c(64.8, 59.0, 66.6, 51.7, 61.1, 54.8)

# your code here 

```
:::

::: {.callout-tip collapse="true"}
#### Solution - More arithmetic

```{r}
#| output: false
#| label: answer-more-arithmetic
# 1
weight_kg <- weight_lbs * 0.4536
# 2
height_m <- height_in * 0.0254
# 3
bmi_2 <- weight_kg / height_m^2
# 4
703 * weight_lbs / height_in^2
# 5
mean(bmi_2)
mean(laryngoscope$BMI)
```

The second group (`bmi_2`) have a lower mean BMI, 39.6, than the `laryngoscope` patients, 41.9.
:::

::: {.callout-note icon="false"}
#### Task - Fix this code

Revise the code below to produce a result of 172.4.

(Hint: think about why the current result is returned, and what R data structure `mean()` probably expects as its argument.)

```{r}
mean(203.0, 150.1, 102.8, 241.0, 189.1, 148.3)

```
:::

::: {.callout-tip collapse="true"}
#### Solution - Fix this code

```{r}
#| output: false
#| label: answer-fix-code
mean(c(203.0, 150.1, 102.8, 241.0, 189.1, 148.3))
```

`mean()` expects a vector, so combine the values into a single vector first using `c()`.
:::
