---
title: "ICA 2.1 Pipes, selecting and sorting"
format: 
  html:
    self-contained: true
    embed-resources: true
  gfm: default
editor: visual
---

```{r}
#| output: false
library(tidyverse)
polyps <- read_csv("data/polyps.csv")
```

#### Task 1 - Use the pipe operator

\(1\) Rewrite the wrapped calls below to use the pipe operator. Make sure that you get the same result.

```{r}
round(mean(c(265, 357, 154, 282, 173)), 0)

paste(signif(mean(polyps$age), 2), "years avg. age")


```

\(2\) Consider the values below. Using the pipe operator, write the code to calculate their standard deviation ($\sigma$) and then the standard error of the sample ($s$ or $\mathrm{SE}$) using the equation: $\mathrm{SE} = \frac{\sigma}{\sqrt{n}}$ , rounded to two decimal places. $n =$ number of values in sample.

```{r}
c(158.4, 176.8, 162.7, 169.6, 163.0, 165.3, 134.3, 190.7)
```

#### Task 2 - Select variables of interest

\(1\) Get the variable names (column names) of `polyps`. How many are there? (Hints: `names()` and `length()`)

\(2\) Suppose we only want to examine the baseline, treatment, and 3-month polyp counts for a regression. Use the previous question's result with `dplyr::select()` to return a data frame that has only these three columns.

```{r}
# 🅿
# your code here 
```

\(3\) Consider the first, third, and fifth columns. What would you predict their names to be? Now, write a `select()` statement that selects these columns using numerical indices, and check your prediction.

```{r}

```

\(4\) A collaborator tells you that the 12-month numbers are incomplete and need to be revised from another spreadsheet. They ask you to return all of the columns *except* for the 12-month numbers.

```{r}

```

#### Task 3 - Arrange rows for browsing

\(1\) You are curious about the age makeup of the group. Use `dplyr::arrange()` to return `polyps` sorted by age.

```{r}
# 🅿
# your code here 

```

\(2\) To avoid bias, you also want to browse the data in reverse age order. Unfortunately, you can't remember how to do that with `arrange()`. Run `?arrange` to find the solution in the function documentation. (Hint: you want to modify the *argument* you're giving to `arrange()`; check the Arguments section.) Then, write the code below and check your answer.

```{r}

```

\(3\) Now you choose to sort by treatment group. However, since there are only two groups, more sorting might be desirable. Write the code for this and add the 3-month polyp count, descending, as a second sort.

```{r}

```

\(4\) Consider the previous results. Now try reversing the sort order---3-month count descending, and then treatment group---and see how the data read differently.

```{r}

```
