---
title: "ICA 5.2 pivoting"
format: 
  html:
    self-contained: true
    embed-resources: true
  gfm: default
editor: visual
---

Attach the tidyverse and medicaldata packages here:

```{r}
#| output: false
#| echo: true
library(tidyverse)
library(medicaldata)
```

Task 1 - Pivot polyp counts (baseline and 12-month) longer

\(1\) Consider `medicaldata::polyps`. What is the table's current observational unit?

\(2\) Suppose we want to treat `baseline, number3m, and number12m` as separate observations---in other words, all polyp counts would go into a single column, and a new column would be added for `visit`. How many rows would we have for each patient?

\(3\) Use `dplyr::pivot_longer()` to move the three polyp counts from columns into rows. Your result should have `visit` and `polyp_count` columns (`polyp_count` is where the value goes). Assign the result to a new object. Examine the data frame and confirm that it has the expected row count.

```{r}
# 🅿
?pivot_longer
data(polyps)
polyps %>% 
  pivot_longer(cols=c(baseline, number3m, number12m),
               names_to="visit",
               values_to="polyp_count") %>% 
  mutate(visit = as_factor(visit)) %>% 
  ggplot() + 
  geom_boxplot(aes(x=polyp_count, y=visit))
```
