---
title: "ICA 4.2 New variables, faceting"
format: 
  html:
    self-contained: true
    embed-resources: true
editor: visual
---

Attach the tidyverse and medicaldata packages here:

```{r}
#| output: false
#| echo: true
library(tidyverse)
library(medicaldata)
```

#### Task 1 - Calculate a column

(1) In `medicaldata::smartpill`, use `dplyr::mutate()` to calculate a new `BMI_metric` variable, using `Height` and `Weight`. Make mental note of the units involved (`?smartpill` may help). Assign the result to a new object called `sp`.

```{r}
# 💊

```

(2) Let's try converting these variables to English units. In `sp`, mutate new `Height_in` and `Weight_lbs` columns, using the existing data as basis. Make sure to store the successful result back into `sp`.

```{r}

```

(3) Mutate a new `BMI_english` column using the English-converted units from step 2. Use `dplyr::select()` to easily compare your two BMI calculations side by side.

```{r}

```

#### Answer 1 - Calculate a column

```{r}
#| output: false
#| label: answer-calc-column
# 1
sp <- smartpill %>% 
  mutate(BMI_metric = Weight/(Height*.01)^2,
         .after=Weight)
# 2
sp %>% 
  mutate(Height_in = Height*0.3937,
         Weight_lbs = Weight*2.205,
         .after=BMI_metric)
# 3
  
```

#### Task 2 - Inclusion criterion

(1) After consulting the polyps experimental protocol, you find that patients must participate in the full 12 months in order to be included in the analysis. The PI would like you to create a new logical (T/F) variable called `inclusion`. Check whether `number12m` is `NA` or not, and calculate an appropriate T/F value for each patient. Assign the successful result to a new object `pol`.

(2) Filter `pol` for cases to include, based on the new `inclusion` column.

```{r}
# 🅿

```

#### Answer 2 - Inclusion criterion

#### Task 3 - Age groups

(1) Use numeric and visual summary function(s) to see what the spread of ages is in `smartpill`. (Hints: `summary()`, `ggplot2::geom_histogram()`, `hist()`)

(2) Suppose we want to establish a new variable called `age_group`. Using `mutate()` and `case_when()`, assign each patient to the appropriate ranged group: 0-30, 31-40, 41-50, 51-100. Assign the successful result to `sp`. (Note: if you use `smartpill`, rather than `sp` from previous exercise, as starting point to do this work, you will overwrite the recent columns!)

(3) Use `group_by()` and `summarize()` to see how many patients are in each age group. Does this seem roughly congruent with what you saw in step 1?

```{r}
# 💊

```

#### Answer 3 - Age groups
