---
title: "ICA 1.2 Loading and addressing data"
format: 
  html: 
    self-contained: true
    embed-resources: true
editor: visual
---

::: {.callout-note icon="false"}
#### Task - Object assignment

1.  Supplement the code below so that the values are assigned into an object called `height`.
2.  To see a representation of `height`, type its name on a line by itself and then run the line (Ctrl-Enter or ⌘-Enter). Try this now. `print(obj_name)` (which "prints" to the screen) and `show(obj_name)` do the same, where `obj_name` is the object of interest.
3.  Consider `length(height)`. What do you think will be the result of this call? Add it to the chunk below and test your prediction.

💡 Tip: The keyboard shortcut for inserting the assignment operator is **`Alt -`** (*alt-hyphen*) on Windows, or **`⌥ -`**(*option-hyphen*) on Mac.

```{r}
c(158.4, 176.8, 162.7, 169.6, 163.0, 165.3, 134.3, 190.7)
signif(rnorm(8, 161.3, .19*sqrt(5510)), 4)
# your code here 
```
:::

::: {.callout-tip collapse="true"}
#### Solution - Object assignment

```{r}
#| output: false
#| label: answer-object-assignment
# 1
height <- c(158.4, 176.8, 162.7, 169.6, 163.0, 165.3, 134.3, 190.7)

# 2
height
# or:
print(height)

# 3
length(height)
```

The result is 8 because there are 8 values in the `height` vector.
:::

::: {.callout-note icon="false"}
#### Task - Attach a package

Let's attach the readr package to load the CSV file. Call `library(readr)` below.

```{r}

```
:::

::: {.callout-tip collapse="true"}
#### Solution - Attach a package

```{r}
#| output: false
#| label: answer-attach-package
library(readr)
```

Note that many packages have *dependencies*, meaning that they must attach and utilize other packages in order order to function.
:::

::: {.callout-note icon="false"}
#### Task - Load a CSV as a data frame

Let's load some data from a study which treated polyps.

1.  Examine your file system (you can use the Files tab at bottom-right, or Explorer/Finder) for a directory within our project called `data`. Confirm that `data` contains a file called `polyps.csv`.
2.  Use readr's `read_csv()` function to load `polyps.csv`, and assign the result to an object called `polyps`.
3.  Call the object's name to see a representation of it, and confirm you have loaded the file.

```{r}
# 🅿
# your code here 
```
:::

::: {.callout-tip collapse="true"}
#### Solution - Load a CSV as a data frame

```{r}
#| output: false
#| label: answer-load-csv
polyps <- read_csv("data/polyps.csv")
polyps
```
:::

::: {.callout-note icon="false"}
#### Task - A data frame's names

Try calling `names()` on your `polyps` data frame. What do you think this function does? Why might this be useful?

```{r}
# 🅿
# your code here 
```
:::

::: {.callout-tip collapse="true"}
#### Solution - A data frame's names

```{r}
#| output: false
#| label: answer-df-names
names(polyps)
```

`names()` tells us the variable (column) names held in a data frame. This is helpful for
:::

::: {.callout-note icon="false"}
#### Task - Address a variable

1.  Recall that **`$`** allows us to reference a variable in a data frame. For example, suppose we had an ecology dataset called `penguins`, with a variable called `body_mass_g`. To access the variable, we could type: `penguins$body_mass_g`.
2.  Use the `$` selector below with the information from `names(polyps)` to print the participant ages as a vector. (Hint: `df_name$variable_name` is the format you want.)
3.  Assign these values to a new object called `ages`.
4.  Print `ages` to the screen.

```{r}
# 🅿
# your code here 
```
:::

::: {.callout-tip collapse="true"}
#### Solution - Address a variable

```{r}
#| output: false
#| label: answer-address-variable
polyps$age
ages <- polyps$age
ages
```
:::

::: {.callout-note icon="false"}
#### Task - Arithmetic with variables

1.  Calculate the mean of `ages`, rounded to two significant digits.
2.  Calculate participant ages in months.
3.  `baseline` and `number3m` are the counts of observed polyps *initially* (baseline), and after *3 months*, respectively. Try subtracting `baseline` from `number3m`. What is this result?
4.  Assign the subtraction result to a new object called `diff_3m`. How many values does `diff_3m` have? Why?
5.  Print `diff_3m` to the screen.

```{r}
# 🅿
# your code here 
```
:::

::: {.callout-tip collapse="true"}
#### Solution - Arithmetic with variables

```{r}
#| output: false
#| label: answer-arithmetic-vars

# 1 
signif(mean(ages), 2)
# 2
ages * 12
# 3
polyps$number3m - polyps$baseline
# 4
diff_3m <- polyps$number3m - polyps$baseline
length(diff_3m)
# 5
diff_3m
```

`diff_3m` is each participant's reduction in polyps after 3 months. There are 22 values in the result because there were 22 values in the input, and subtraction is a vectorized operation.
:::
