---
title: "ICA 3.1 univariate plots"
format: 
  html:
    self-contained: true
    embed-resources: true
editor: visual
---

Attach the tidyverse and medicaldata packages here:

```{r}
#| output: false
#| echo: true
library(tidyverse)
library(medicaldata)
```

::: {.callout-note icon="false"}
#### Task 1 - Histograms

(1) Create a histogram of patient `BMI` in the `laryngoscope` data set.

```{r}
# 🗣
# your code here 
```

(2) Note the visual output as well as the additional messages (one will be about bins). Modify your code from step 1 to add a `binwidth` argument with a value. Experiment until finding a good bin width for the data.

```{r}
# 🗣
# your code here 
```

:::

::: {.callout-tip collapse="true"}
#### Answer - Histograms

```{r}
#| output: false
#| label: answer-histograms
# 1
ggplot(laryngoscope) + 
  geom_histogram(aes(x=BMI))
# 2
ggplot(laryngoscope) + 
  geom_histogram(aes(x=BMI), binwidth=1.5)
```

The warning about non-finite values is OK. These are missing observations which we could filter from our data prior to visualizing.
:::

::: {.callout-note icon="false"}
#### Task 2 - Labels

(1) Write the code for a histogram of `laryngoscope$total_intubation_time` below.
(2) Now we want to modify the default axis and title labels. Run `?labs` to read about the `labs()` function. Jump down to the Examples to see how it is used.
(3) Use `labs()` to customize the x label to read "Total intubation time (seconds)", and y to read "Count" (capitalized).

```{r}
# 🗣
# your code here 

```
:::

::: {.callout-tip collapse="true"}
#### Answer - Labels

```{r}
#| output: false
#| label: answer-labels
?labs
ggplot(laryngoscope) + 
  geom_histogram(aes(x=total_intubation_time), binwidth=4) +
  labs(x="Total intubation time (seconds)",
       y="Count")
```

:::

::: {.callout-note icon="false"}
## Task 3 - Explore variables via histogram

Use `names()` and `geom_histogram()` to explore the distribution of other numeric variables in `laryngoscope` and `polyps`.

```{r}

```
:::

::: {.callout-tip collapse="true"}
#### Answer - Explore variables via histogram

```{r}
#| output: false
#| label: answer-explore
names(laryngoscope)
lp <- ggplot(laryngoscope)
lp + geom_histogram(aes(age))
lp + geom_histogram(aes(BMI))
lp + geom_histogram(aes(ease))

names(polyps)
pp <- ggplot(polyps)
pp + geom_histogram(aes(age))
# etc.
```
:::