---
title: "ICA 3.2 multivariate plots"
format: 
  html:
    self-contained: true
    embed-resources: true
editor: visual
---

Attach the tidyverse and medicaldata packages here:

```{r}
#| output: false
#| echo: true
library(tidyverse)
library(medicaldata)
```

::: {.callout-note icon="false"}
#### Task 1 - Scatter plot

(1) Make a scatter plot comparing `polyps` baseline (x) and number3m (y).
(2) Add a smoother using `geom_smooth()`. Note that this layer will need aesthetics. You can store the aesthetics in the parent plot object rather than each layer if you prefer.
(3) Let's add color to show our two treatment groups. Add a `color` argument to `aes()` with `treatment` (our variable of interest) as the value.

```{r}
# 🅿
# your code here 
```
:::

::: {.callout-tip collapse="true"}
#### Answer - Scatter plot

```{r}
#| output: false
#| label: answer-scatter
# 1
pp <- ggplot(polyps)
pp + geom_point(aes(x=baseline, y=number3m))
# 2
pp + geom_point(aes(x=baseline, y=number3m)) +
  geom_smooth(aes(x=baseline, y=number3m))
# 3
ggplot(polyps, aes(x=baseline, y=number3m, color=treatment)) +
  geom_point() +
  geom_smooth()
```

:::


::: {.callout-note icon="false"}
#### Task 2 - Bar chart

(1) Compare the number of subjects in each `polyps` treatment group using a bar chart.
(2) Change the chart's orientation using the x and y aesthetic mappings.

```{r}
# 🅿
# your code here 
```
:::

::: {.callout-tip collapse="true"}
#### Answer - Bar chart

```{r}
#| output: false
#| label: answer-bar-chart
# 1
ggplot(polyps) + geom_bar(aes(x=treatment))
# 2
ggplot(polyps) + geom_bar(aes(y=treatment))
```

:::


